%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)	
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
%\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{kotex}
\usepackage{hyperref}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Sungju Kim} % Your name at the top

 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\moveleft.5\hoffset\centerline{goddoe2@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Education
%---------------------------------------------------------------------------------------- 

\section{EDUCATION}

{\bf Kyungpook National University}, Computer Science, M.S. \hfill 2014.03 - 2016.02 \\
Computer \& Robot Vision Lab, Daegu, South Korea

{\bf Kyungpook National University}, Biotechnology, B.S.  \hfill 2009.03 - 2014.02 \\
Daegu, South Korea



%----------------------------------------------------------------------------------------
%	Experience
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}  

{\bf NAVER Cloud}, Tech lead \hfill 2023.01 - Present \\
Hyperscale AI, Seongnam, South Korea \\
\begin{itemize}
\item Contributed to HyperCLOVA X 32B Think (https://arxiv.org/pdf/2601.03286) through model development and research for SWE Agents, including creating SFT and RL datasets, developing training environments for SWE Agent RL, and babysitting model training during the General and SWE Agent RL phases. 2025
\item Contributed as one of the core contributors to the \href{https://arxiv.org/abs/2506.22403}{HyperCLOVA X THINK Project}. 2025
\item  Led a team that developed a product and model similar to GitHub Copilot, which is used by internal developers at NAVER. 2023-2024
\item Contributed as one of the technical leads to the \href{https://arxiv.org/abs/2404.01954}{HyperCLOVA X project}. 2024
\item  Contributed to the enhancement of the coding capabilities for HyperCLOVA X, an LLM developed by NAVER Cloud.2023-2024
\end{itemize}
{\bf NAVER}, Tech lead \hfill 2022.08 - 2022.12 \\
{\bf NAVER}, AI Research Engineer, NLP \hfill 2018.07 - 2022.07 \\
Clova AI assistant team, Seongnam, South Korea \\
\begin{itemize} 
\item Developed a state-of-the-art Neural Information Retrieval model using NAVER's extensive internal text data resources, achieving unprecedented performance in zero-shot information retrieval. 2022.
\item Contributed to develop a large-scale autoregressive language model, HyperCLOVA. My contributions included data collection, purification, and conducting experimental work on zero-shot, few-shot, and p-tuning. 2020-2021.
\item Developed Pretrained Language Models for Korean and Japanese. 2020-2021.
\item Developed Out of Domain Detection model for dialogue system using sentence-embedding model. 2020-2021
\item Developed Natural Language Understanding model. 2020.
\item Developed and implemented a suggestion model for ambiguous user queries, significantly enhancing the system's capacity to interpret and respond to a broad spectrum of unclear queries. 2018-2019.
\item Improved dialogue manager of dialogue system. 2018-2019.
\end{itemize}


{\bf Nomad Connection}, AI researcher \hfill 2016.02 - 2018.07 \\
AI lab team, Seoul, South Korea
\begin{itemize} 
\item Modeling intent classifier and sentence encoder for AI chatbot. 2017-2018.
\item Developed Keyword extractor and Sentiment classifier. 2016-2017.
\item Developed ID card OCR model development for non-face-to-face authentication. 2017.
\item Developed Sentiment classifier. 2016
\end{itemize}


%----------------------------------------------------------------------------------------
%	Activity
%----------------------------------------------------------------------------------------

\section{AWARD} 
{\bf Ecothon, Grand Prize (1st place), Awarded by the Minister of Environment} \\
Team Qualc, 2016
\begin{itemize}
\item IOT smart oil filter for life management of vehicle's oil filter.
\item News: \href{http://news.naver.com/main/read.nhn?mode=LSD&mid=sec&oid=030&aid=0002533677&sid1=001&lfrom=kakao}{Ingenious ‘Environment + ICT’ Startup Idea Competition Ecothon… Qualc Team Grand Prize (title translated)}.
\end{itemize}
 

%----------------------------------------------------------------------------------------
%	Publication
%----------------------------------------------------------------------------------------

\section{SELECTED PUBLICATIONS} 

HyperCLOVA X Team, ..., \underline {SJ Kim} et al, {\bf HyperCLOVA X THINK 32B}, arXiv preprint arXiv:2601.03286, 2025.

HyperCLOVA X Team, ..., \underline {SJ Kim} et al, {\bf HyperCLOVA X THINK Technical Report}, arXiv preprint arXiv:2506.22403, 2025.

KM Yoo, ..., \underline {SJ Kim} et al, {\bf HyperCLOVA X Technical Report}, arXiv preprint arXiv:2404.01954, 2024.

\underline {SJ Kim}, SH Kim, J Park, KM Yoo, IH Kang, {\bf The Bi-Cross Pretraining Method to Enhance Language Representation}, Proceedings of the 33th Annual Conference on Human and Cognitive Language Technology, 2021.

BS Kim, ..., \underline {SJ Kim} et al, {\bf What Changes Can Large-scale Language Models Bring? Intensive Study on HyperCLOVA: Billions-scale Korean Generative Pretrained Transformers}, Proceedings of the 2021 Conference on Empirical Methods in Natural Language Processing, 2021

\underline{SJ Kim}, SB Suh, JS Park, SH Park, DH Jeon, SH Kim, KD Kim, IH Kang, {\bf Self-supervised Learning Method using Heterogeneous Mass Corpus for Sentence Embedding Model}, Proceedings of the 32th Annual Conference on Human and Cognitive Language Technology, 2020.

\underline{SJ Kim}, WW Kim, YS Seol, IH Kang, {\bf Cross Gated Mechanism to Improve Natural Language Understanding}, Proceedings of the 31th Annual Conference on Human and Cognitive Language Technology., 2019.

\underline{SJ Kim} and SY Park, {\bf Lane-Level Positioning based on 3D Tracking Path of Traffic Signs}, in Proceedings of the 11th Joint Conference on Computer Vision, Imaging and Computer Graphics Theory and Applications - Volume 3: VISAPP, (VISIGRAPP 2016), 2016.

\section{PATENTS}  

\begin{itemize}
  \item \textbf{Method, Apparatus and Computer Program for Providing Coding Environment Optimzied for Each User} \\
  \textit{KR Patent Application No. 1020230177976}, , Published as KR1020250088172A in 2025 \\
  \href{https://doi.org/10.8080/1020230177976}{DOI Link}

  \item \textbf{Method and System for Processing Unclear Intent Query in Conversation System} \\
  \textit{US Patent No. US11403345B2}, Granted in 2022 \\
  \href{https://patents.google.com/patent/US11403345B2}{Google Patents Link}
\end{itemize}
\section{LINKS}  

github: \href{https://github.com/goddoe}{https://github.com/goddoe} \\
linkedin: \href{https://www.linkedin.com/in/sungju-kim-3b0406b0/}{https://www.linkedin.com/in/sungju-kim-3b0406b0/}


%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
